\documentclass[12pt, letterpaper]{article}
\usepackage{SyllabusStyle}

\begin{document}
\begin{center}
	{\Large \textsc{Introduction to Chemistry Lab}}

	CHEM 1015
\end{center}

\begin{center}
	{\large Fall 2024}
\end{center}
\begin{center}
	\rule{0.99\textwidth}{0.4pt}
	\begin{tabular}{llcll}
		\textbf{Instructor:} & Matthew Rowley           &  & \textbf{Office Hours:} & Daily 10:00 am -- 11:00 am \\
		\textbf{Telephone:}  & (435) 586-7875           &  &                        &  \\
		\textbf{Email:}      & matthewrowley$1$@suu.edu &  & \textbf{Office:}       & SC-220                   \\
		\multicolumn{5}{c}{Please include the course number in the subject line of all correspondence.}
	\end{tabular}
	\rule{0.99\textwidth}{0.4pt}
\end{center}

\section*{Tentative Schedule}
This class will meet on Wednesdays from 2:00--3:50 am in room 010 of the Science Center (SC)

\paragraph{Week 1: Aug. 28 -- Aug. 30}~

\textbf{No lab this week!}

\paragraph{Week 2: Sep. 2 -- Sep. 6}~

\textbf{No lab this week!}

\paragraph{Week 3: Sep. 9 -- Sep. 13}~

Experiment 1: Safety in the Lab

\paragraph{Week 4: Sep. 16 -- Sep. 20}~

Experiment 2: Lab Techniques and Measurements

\paragraph{Week 5: Sep. 23 -- Sep. 27}~

Demonstration 1: Physical Techniques

\paragraph{Week 6: Sep. 30 -- Oct. 4}~

Demonstration 2: Chemical Reactions

\paragraph{Week 7: Oct. 7 -- Oct. 11}~

Experiment 3: Chemical Reactions

\paragraph{Week 8: Oct. 14 -- Oct. 18}~

\textbf{Do not come to lab this week -- Fall Break!}

\paragraph{Week 9: Oct. 21 -- Oct. 25}~

Demonstration 3: Conductivity of Aqueous Solutions

\paragraph{Week 10: Oct. 28 -- Nov. 1}~

Experiment 4: Preparation and Properties of Oxygen

\paragraph{Week 11: Nov. 4 -- Nov. 8}~

Demonstration 4: Chemical Kinetics

\paragraph{Week 12: Nov. 11 -- Nov. 15}~

Experiment 5: Physical and Chemical Properties of Alkanes and Alkenes

\paragraph{Week 13: Nov. 18 -- Nov. 22}~

Demonstration 5: Polymers

-and-

Demonstration 6: Boyle's Law

\paragraph{Week 14: Nov. 25 -- Nov. 29}~

\textbf{No lab this week -- Thanksgiving Break!}

\paragraph{Week 15: Dec. 2 -- Dec. 6}~

\textbf{Final Exam}

\paragraph{Finals Week}~

No Final -- You took it last week!

\end{document}
